Recent advances in random matrix theory applied to heavy-tailed multivariate time series

### 2015-08-10 papers/Number1/paper.tex
Revised the review part.

\subsection{Overview of light-tailed case}
Yin, Bai and Krishnaiah proved in their 1988 paper
\cite{yin:bai:Krishnaiah:1988} the followng result for a $p \times n$
matrix $\bf W$ with iid entries $w_{ij}$ under the assumption $\E
w_{11} = 0$ and $\E w_{11}^4 < \infty$.
\[
\lim_{n \to \infty} \lambda_{\M}\left({1 \over n}\bf{WW'}\right) = \left(
  1 + \sqrt{p \over n}
\right)^2 \E w_{11}
\]

@@

>>>>

\subsection{Overview of light-tailed case}
Yin, Bai and Krishnaiah proved in their 1988 paper
\cite{yin:bai:Krishnaiah:1988} the followng result for a $p \times n$
matrix $\bf X$ with iid entries $X_{ij}$ under the assumption $\E
X_{11} = 0$ and $\E x_{11}^4 < \infty$.
\[
\lim_{n \to \infty} \lambda_{\M}\left({1 \over n}\bf{XX'}\right) = \left(
  1 + \sqrt{p \over n}
\right)^2 \E x_{11}
\]
Later on, several authors \cite{Pillai:Yin:2011, tao:vu:2012,
  Wang:2012} looked into empirical covariance matrix $S_{n, p} = {1
  \over n} \bf{XX}'$, where the entries of $\bf X$, denoted $x_{ij}$
are independent and have an exponential decay: $\exists B_1, B_2 > 0$
such that
\begin{equation}
  \label{eq:C0}
  \forall i \in \{1, 2, \dots, p\}\text{, }
  \forall j \in \{1, 2, \dots, n\}\text{, }
  \P(|x_{ij}| > t^{B_1}) \leq e^{-t}
\end{equation}
for all $t > B_2$. Pillai and Yin \cite{Pillai:Yin:2011} proved that,
given condition \eqref{eq:C0} and in additon $1 < n/p < \infty$,
the empirical eigenvalues are localized to their theoretical
values: $\exists c, C > 0$ such that $\forall 1 \leq j \leq p$
\[
\P(\left|
  \lambda_{(j)} - \gamma_{j}^{n,p}
\right|) \geq  (\log p)
\]

@@

\bibitem{Pillai:Yin:2011}
{\sc N. Pillai and J. Yin}\ (2011)
Universality of covariance matrices
{\em arXiv:1110.2501,2011}

%K. Wang. Random covariance matrices: universality of local statistics of
%eigenvalues up to the edge. RMTA, 1(1), 2012.
\bibitem{Wang:2012}
{\sc K. Wang}\ (2012)
Random covariance matrices: universality of local statistics of
eigenvalues up to the edge
{\em RMTA} {\bf 1} (1)
